---
title: "Assignment 1"
---

# Assignment 1

My first assignment has Three parts.

## (a)





## (b)

Differences between R and Python:

  1.
  
  R: In R, indices begin at 1. Additionally, it contains special data structures that are ideal for statistical analysis, such as factors, data frames, and vectors.
  
  Python: Python indexes data with a base of 0. Moreover, it makes use of more conventional data structures like sets, dictionaries, and lists. 
  
  2.
  
  R: The syntax of R is designed with statistical data analysis in mind. R code is frequently written in a way that is more functional.
  
  Python: Python is renowned for its readability and boasts a more versatile syntax. For code blocks, it employs indentation (whitespace).
  
  Example:
  
  In R:
  
  ```{r}
  nums <- c(16, 20, 35, 63, 78)
  mean <- mean(nums)
  print(mean)
  ```
  In Python:
  
  ```{py}
  nums = [16, 20, 35, 63, 78]
  mean = sum(nums) / len(nums)
  print(mean)
  ```
  
  3.
  
  R: R uses specific functions and expressions for string processing.
  
  Python: Python provides built-in string methods and libraries for string processing.
  
  Example:
  
  In R:
  
  ```{r}
  text <- "Hello, World!"
  uppercase_text <- toupper(text)
  ```
  
  In Python:
  
  ```{py}
  text = "Hello, World!"
  uppercase_text = text.upper()
  ```
  